The Poisson approximate likelihood compared to the particle filter

### 2024-08-19 ms.Rnw
minor edits on greatlakes

    foreach(j = 1:ncores, .combine = c,
      .options.future = list(seed = 998468235L)
    ) %dofuture% {
      pfilter(
        pfilter_obj[[i]], Np = NP_MIF, save.states = TRUE, params = params_wwr
      )
    } -> pfs
    pfilter_ovov_sim_computation[i] <- logmeanexp(logLik(pfs))  
  }
  pfilter_ovov_sim_computation
}) ->  pfilter_ovov_sim_100
@

>>>>

    foreach(j = 1:ncores, .combine = c,
      .options.future = list(seed = 998468235L)
    ) %dofuture% {
      pfilter(
        pfilter_obj[[i]], Np = NP_MIF, save.states = FALSE, params = params_wwr
      )
    } -> pfs
    pfilter_ovov_sim_computation[i] <- logmeanexp(logLik(pfs))  
  }
  pfilter_ovov_sim_computation
}) ->  pfilter_ovov_sim_100
@
